Carbonate chemistry at Ny-Ålesund

### 2021-05-14 awipev-CO2.Rmd
fixing merge issue 2

slide_dbl(~mean(.x$datetime, .x$co2_air), .before = 3, .after = 3)
  #slide_period_dbl(.x = atm_co2$co2_air, .f = mean, .i = atm_co2$datetime, .period = "month")

#d_all <- dplyr::left_join(d_all, atm_co2, by = "datetime")
p_atm_co2 <- atm_co2 %>% 
  #tidyr::pivot_longer(cols = c(pco2_air, pco2_air_old), names_to = "dataset", values_to = "pco2") %>% 
  ggplot() +
  geom_point(aes(x = datetime, y = running_mean(atm_co2$co2_air, 24)), col = "blue", size = 0.15, na.rm = TRUE) +
  #facet_grid(rows = vars(dataset)) +
  #geom_point(aes(x = datetime, y = pco2_air_old), col = "grey", size = 0.15, na.rm = TRUE) +
  labs(title = "Atmospheric CO2 at Zeppelin", x = "Time", y = "CO2 (ppm)") +
  Mytheme(size_labs = 8)
p_atm_co2
ggsave(filename = "figures/atm_co2.png", plot = p_atm_co2, width = 20, units = "cm")
```

>>>>

slide_dbl(~mean(.x$datetime, .x$co2_air), .before = 3, .after = 3)
  #slide_period_dbl(.x = atm_co2$co2_air, .f = mean, .i = atm_co2$datetime, .period = "month")
#d_all <- dplyr::left_join(d_all, atm_co2, by = "datetime")
p_atm_co2 <- atm_co2 %>% 
  #tidyr::pivot_longer(cols = c(pco2_air, pco2_air_old), names_to = "dataset", values_to = "pco2") %>% 
  ggplot() +
  geom_point(aes(x = datetime, y = running_mean(atm_co2$co2_air, 24)), col = "blue", size = 0.15, na.rm = TRUE) +
  #facet_grid(rows = vars(dataset)) +
  #geom_point(aes(x = datetime, y = pco2_air_old), col = "grey", size = 0.15, na.rm = TRUE) +
  labs(title = "Atmospheric CO2 at Zeppelin", x = "Time", y = "CO2 (ppm)") +
  Mytheme(size_labs = 8)
p_atm_co2
ggsave(filename = "figures/atm_co2.png", plot = p_atm_co2, width = 20, units = "cm")
```
